\LARGE \bf\vspace{-10mm} Face Recognition: Too Bias, or Not Too Bias?

### 2020-02-06 sections/analysis.tex
wip

% \vspace{-2pt}
\subsection{Score Analysis}
Fig.~\ref{fig:detection-model} shows score distributions for faces of the same identity (\ie \emph{Genuine}) and different (\ie \emph{Imposter}), with \gls{sdm}s split by subgroup. Observe that scores of imposters  approximately distribute about a peak of zero independent of subgroup, with slightly different standard deviation. Observe that the broadness in score distribution of the \emph{genuine} pairs varies across subgroups. Asian Fem
Fig.~\ref{fig:confusion} shows the confusion matrix of the subgroups. A vast majority of errors occurs in intra-subgroup. It is interesting to note that while the definition of  each group  based on ethnicity and race may not be crisply defined, the confusion matrix indicates that in practice the \gls{cnn} finds that the groups are effectively separate. The categories are, therefore, meaningful in the context of \gls{fr}.

@@

\begin{figure}[t!] 
	\centering    
	\includegraphics[width=\linewidth] {images/human_eval.pdf}
		\caption{\small{\textbf{Qualitative results of human assessment.} $\checkmark$ for \emph{match}; $\times$ for \emph{non-match}, which scores plotted next to each. Humans tend to be more successful at recognizing their own subgroup, with few exceptions (bottom). }}
		% (\eg bottom row). } Result summary in Table~\ref{tab:human-eval}.
		\label{fig:human-eval} 
		\vspace{-5mm}
\end{figure}

% \vspace{-5pt}
\subsection{Human evaluation}
 Quantitative and qualitative results are in Table~\ref{tab:humsn-eval-results} and Fig.~\ref{fig:human-eval}, respectfully. One might expect that the most exposure to others would be within the same subgroup, and, therefore, would be best at labeling their own. Secondarily, they would be best at labeling images of the same ethnicity, but opposite gender. Our findings concur. Each subgroup is best at labeling their type, and then second best at labeling the same ethnicity but opposite sex. Interestingly, each group of images is best tagged by the corresponding subgroup, with the second-to-best having the same ethnicity and opposite gender. On average, subgroups are comparable at labeling images.

>>>>

% \vspace{-2mm}
% \vspace{-2pt}
\subsection{Score Analysis}
Fig.~\ref{fig:detection-model} shows score distributions for faces of the same (\ie \emph{Genuine}) and different (\ie \emph{Imposter}) identity, with a subgroup per \gls{sdm} plot. Notice that score distributions for imposters tends to peak about zero for all subgroups, and with minimal deviation comparing modes of the different plots. On the other hand, the score distribution of the \emph{genuine} pairs varies across subgroups in location (\ie score value) and spread (\ie overall shape). Asian Fem
Fig.~\ref{fig:confusion} shows the confusion matrix of the subgroups. A vast majority of errors occurs in intra-subgroup. It is interesting to note that while the definition of  each group  based on ethnicity and race may not be crisply defined, the confusion matrix indicates that in practice the \gls{cnn} finds that the groups are effectively separate. The categories are, therefore, meaningful in the context of \gls{fr}.

@@

\begin{figure}[t!] 
	\centering    
	\includegraphics[width=\linewidth] {images/human_eval.pdf}
		\caption{\small{\textbf{Qualitative results of human assessment.} $\checkmark$ for \emph{match}; $\times$ for \emph{non-match}, which scores plotted next to each. Humans tend to be more successful at recognizing their own subgroup, with few exceptions (bottom). }}
		% (\eg bottom row). } Result summary in Table~\ref{tab:human-eval}.
		\label{fig:human-eval} 
		\vspace{-5mm}
\end{figure} 
\vspace{-2mm}
% \vspace{-5pt}
\subsection{Human evaluation}
 Quantitative and qualitative results are in Table~\ref{tab:humsn-eval-results} and Fig.~\ref{fig:human-eval}, respectfully. One might expect that the most exposure to others would be within the same subgroup, and, therefore, would be best at labeling their own. Secondarily, they would be best at labeling images of the same ethnicity, but opposite gender. Our findings concur. Each subgroup is best at labeling their type, and then second best at labeling the same ethnicity but opposite sex. Interestingly, each group of images is best tagged by the corresponding subgroup, with the second-to-best having the same ethnicity and opposite gender. On average, subgroups are comparable at labeling images.
